---
title: "Chapter 5 HW"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---


###**_Problem 28_**

###**a) Is there substantial evidence (alpha = .01) that the additive reduces the mean absorption from its current value?**
    
####_Hypotheses:_  
    
* H_0: mu = 35
    
* H_A: mu < 35

####_Test Statistic:_

* z = (y_hat - mu)/(sigma/sqrt(n))

```{r, echo = FALSE}
test_stat <- round((33.6-35)/(9.2/sqrt(50)), 4)
paste0("My test statistic is z =", test_stat)
```

####_P-value:_

```{r, message = FALSE, warning = FALSE}
require(BSDA)
sample <- rep(33.6, times = 50)
test <- z.test(x = sample, sigma.x = 9.2, alternative = "less", mu = 35, conf.level = 0.99)
```

####_Conclusion:_  

  Because our p-value(0.141) > 0.01, there is _not_ sufficient evidence to reject the null hypothesis that the mean absorption rate = 35 units.  The data from the sample do _not_ provide enough proof at the 99% level that the additive brings down the mean absorption rate.  


###**b) What is the level of significance of your test results?**

```{r, echo = FALSE}
paste("My p-value from my test was", round(test$p.value, 4))
```

###**d) Estimate the mean absorption using a 99% confidence interval.  Is the confidence interval consistent with your conclusions from the hypothesis test?**

####_Confidence Interval_

```{r, echo = FALSE}
confidence_int <- c(round(mean(sample)- qnorm(.01, 0,1)*(9.2/sqrt(length(sample))), 4), round(mean(sample) + qnorm(0.01, 0, 1)*(9.2/sqrt(length(sample))), 4))
paste0("My Confidence Interval at the 99% level is between (", confidence_int[2], " and ", confidence_int[1], ")")
```

####_Conclusion_  

  Since my y-hat sits between the two values of my confidence interval, this method backs up my hypothesis. 

###**_Problem 41_**

###**a) Place a 95% confidence on the mean dissolved oxygen level during the 2-month period.**

```{r, echo = FALSE}
data <- c(5.1, 4.9, 5.6, 4.2, 4.8, 4.5, 5.3, 5.2)

conf_interval <- c(round(mean(data)-qnorm(0.025,0,1)*(sd(data)/sqrt(length(data))), 4) , round(mean(data)+qnorm(0.025, 0,1)*(sd(data)/sqrt(length(data))), 4))
paste0("My confidence interval at 95% is between (", conf_interval[2], " and ", conf_interval[1], ")")
```

###**b) Using the confidence interval from part (a), does the mean oxygen level appear to be less than 5 ppm?**

####_Conclusion:_  

  Since our confidence interval _included_ 5 in the interval, it does not appear, at the 95% level, the mean is less than 5 ppm.  


###**c) Test the research hypothesis that the mean oxygen level is less than 5 ppm.  What is the level of significance of your test?  Interpret your findings.**

####_Hypotheses:_

* H_0 : mu = 5 ppm
* H_A : mu < 5 ppm
  
  + Test at the 95% Level (5% level of significance/alpha)

####_Test Statistic_
```{r, echo = FALSE}
test_stat <- (mean(data) - 5)/(sd(data)/sqrt(length(data)))
paste0("My test statistic is z = ", round(test_stat, 4))
```

####_P-value_


```{r, echo = FALSE}
results <- z.test(x = data, alternative = "less", mu = 5, conf.level = 0.95, sigma.x = sd(data))
paste0("My p-value is ", round(results$p.value, 4))
```

####_Conclusion_
Since my p-value is greater than 0.05, there is _not_ significant evidence to reject the null hypothesis that mu = 5 ppm.  Thus, there is not sufficient evidence that the mean oxygen level is less than 5 ppm.  

