\documentclass{article}

\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}

\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{titlesec}
\usepackage{amsmath}

\setcounter{secnumdepth}{4}

\hypersetup{
    colorlinks=true,     
    urlcolor=magenta
}

\renewcommand{\qedsymbol}{\rule{0.7em}{0.7em}}

\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\setlength{\parskip}{0em}

\newenvironment{blockquote}{%
  \par%
  \vskip1em
  \leftskip=2em\rightskip=2em%
  \noindent\ignorespaces}{%
  \par\vskip1em}

\newenvironment{blockquote2}{%
	\par%
	\vskip1em
	\leftskip=4em\rightskip=4em%
	\noindent\ignorespaces}{%
	\par\vskip1em}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LO]{STA5076}
\fancyhead[RO]{Kyle Ligon}
\fancyfoot[LO]{Chapter 5}
\fancyfoot[RO]{\thepage}
 
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\begin{document}
\section*{Chapter 5 Homework}
\subsection*{Due 2-4-2018}
\subsubsection*{Problem 5.28}
\subsubsection*{a) Is there substantial evidence (alpha = 0.01) that the additive reduces the mean absorption from its current value?}
Hypothesis
\begin{blockquote}
	$H_0: \ \mu = 35$ \\
	$H_{a}: \ \mu < 35$ 
\end{blockquote}
Test Statistic
\begin{blockquote}
	With an n = 50, we can assume a z test statistic will be appropriate.  
	$z_0 = \frac{\bar{y}-\mu_0}{\sigma/\sqrt{n}} = \frac{33.6-35}{9.2/\sqrt{40}} = -1.076$
\end{blockquote}
Rejection Region
\begin{blockquote}
Reject if $z_0 \le z_\alpha$ ; $z_{0.01}=-2.575$
\end{blockquote}
P-Value
\begin{blockquote}
With a confidence level of 99\% to compare to, my P-value ends up being 0.141.  
\end{blockquote}
Conclusion / Interpretation
\begin{blockquote}
	We fail to reject the null hypothesis.  There is not sufficient evident to suggest that the number of improperly issued tickets is less than 35.  
\end{blockquote}
\subsubsection*{b) What is the level of significance(p-value) of your test results?}
\begin{blockquote} The level of significance(p-value) is 0.141.
\end{blockquote}
\subsubsection*{d) Estimate the mean absorption using a 99\% confidence interval.  Is the confidence interval consistent with your conclusions wform the hypothesis test?}
Confidence Interval
\begin{blockquote}
\begin{equation}
	C.I. = \bar{y} \pm z_{1-\frac{\alpha}{2}}(\frac{\sigma}{\sqrt{n}})
\end{equation}
Where our s = 9.2, 
\end{blockquote}
Conclusion
\begin{blockquote}
Since my $\mu = 35$ sits between the two values of my confidence interval, this fits my Conclusion to my hypothesis test that we don't have significant enough data to reject the Null Hypothesis.  
\end{blockquote}
\pagebreak
\subsection*{Problem 41}
\subsubsection*{a) Place a 95\% confidence on the mean dissolved oxygen level during the 2-month period.}
Confidence Interval
\begin{blockquote}
Since my sample size is small (n = 8) and I don't have $\sigma$, I'll leverage a confidence interval based on Student's t Distribution.   
\end{blockquote}
Equation
\begin{equation}
C.I. = \bar{y} \pm t_{1-\frac{\alpha}{2}}(\frac{s}{\sqrt{n}})
\end{equation}

$\bar{y} = 4.95,$
$s = 0.45,$
$n = 8,$
$t_{1-\frac{\alpha}{2}} = 2.365$
\begin{equation}
C.I. = 4.95 \pm 2.365(\frac{0.45}{\sqrt{8}})
\end{equation}
\begin{equation}
C.I. \approx (4.5737, 5.3263)
\end{equation}

\subsubsection*{b) Using the confidence interval from part (a), does the mean oxygen level appear to be less than 5 ppm?}

Conclusion
\begin{blockquote}
With the left tail of the Confidence Interval being less than 5 ppm, it does appear that the population mean($\mu$) could be less than 5 ppm.  
\end{blockquote}

\subsubsection*{c) Test the research hypothesis that the mean oxygen level is less than 5 ppm.  What is the level of significance of your test?  Interpret your findings.}

Hypothesis
\begin{blockquote}
$H_0: \mu = 5$

$H_A: \mu < 5$
\end{blockquote}

Test Statistic
\begin{blockquote}
Since we used a Confidence Interval based on the t distribution, we will use the same distribution just as a 95\% Hypothesis Test since it wasn't stated in the problem.  
\begin{equation}
t=\frac{\bar{y}-\mu_0}{s/\sqrt{n}}
\end{equation}
\begin{equation}
t=\frac{4.95-5}{0.45/\sqrt{8}}
\end{equation}

\begin{equation}
t = -0.314
\end{equation}
\end{blockquote}

Rejection Region
\begin{blockquote}
Since this is a one-sided t-test, we will check what the rejection region is for a t distribution with 7 degrees of freedom and an $\alpha$ of 0.05.  

The rejection region for the Null Hypothesis would be any t-score $\le$ -1.895.  
\end{blockquote}

P-value
\begin{blockquote}
Additionally, the p-value of such a t = -0.314 
\end{blockquote}

Conclusion / Interpretation
\begin{blockquote}
\end{blockquote}




\end{document}

















