---
author: "Kyle Ligon"
title: "Initial Analysis"
output:
  pdf_document: default
  html_document: default
---



###Read the data in and library calls
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(zoo)
library(lubridate)
library(gridExtra)

crime <- read_csv("BPD_Part_1_Victim_Based_Crime_Data.csv", progress = FALSE)
```

###Looking at the data
```{r}
head(crime)

names(crime)
```
Looks like we have information about the crime, where it happened, when it happened, what happened in the form of Description, and the responding Post.  

###Counting up the Number of Crimes
```{r}
descCounts <- crime %>%
                group_by(Description) %>%
                tally() %>%
                arrange(desc(n))
descCounts
```

###Counting up Where the Crimes Occurred
```{r}
hoodCounts <- crime %>%
                group_by(Neighborhood) %>%
                tally() %>%
                arrange(desc(n))
head(hoodCounts)
```
Let's focus on Arsons.  Particurlarly, let's see if the number of Arsons committed in one month are more varied in the winter months than in the other nine months of the year.  For this I will:

\begin{itemize} 

\item Summarize the number of arsons by month

\item Run an F test on number of arsons between the two groups

\item Write a conclusion for the test

\end{itemize}

###1)	Are the distributions of arsons in the winter months less varied that other 9 months?
```{r, warning = FALSE, message = FALSE}
arsons <- crime %>%
            filter(Description == "ARSON")
head(arsons)
```

Checking the dimensions of the new frame
```{r}
dim(arsons)
```
```{r, echo = FALSE, message = FALSE}
arsons_grouped <- arsons %>%
                      mutate(CrimeDate = as.Date(CrimeDate, format = "%m/%d/%Y"),
                             YearMon = as.yearmon(CrimeDate)) %>%
                      group_by(YearMon) %>%
                      summarize(TotalIncidents = sum(`Total Incidents`)) %>%
                      ungroup() %>%
                      mutate(WinterBin = ifelse(substr(YearMon, 1, 3) %in%  c("Dec", "Jan", "Feb"), "Winter",
                                                "SprSumFall"))
ggplot(data = arsons_grouped, aes(x = TotalIncidents)) + geom_histogram(bins = 6) + facet_wrap(~ WinterBin)

var_W <- arsons_grouped %>% filter(WinterBin == "Winter") %>% summarize(Variance = var(TotalIncidents))
var_SSF <- arsons_grouped %>% filter(WinterBin != "Winter") %>% summarize(Variance = var(TotalIncidents))
```
With "normal" distributions, we will proceed with the hypotheses.

Hypotheses:
H_0: var_Winter = var_SprSumFall
H_1: var_Winter < var_SprSumFall

Variance of the Winter Months
```{r, message = FALSE, warning = FALSE}
#degrees of freedom for W 
arsons_grouped %>% filter(WinterBin == "Winter") %>% tally() - 1

var_W
```

Variance of the Other Months
```{r, message = FALSE, warning = FALSE}
arsons_grouped %>% filter(WinterBin != "Winter") %>% tally() - 1

var_SSF
```

Test Statistic for F Test
```{r, warning = FALSE, message = FALSE}
f <- as.numeric(round(var_W/var_SSF, 4))
f
```

Rejection Region
```{r, warning = FALSE, message = FALSE}
qf(0.975, 16, 51)
f < qf(0.025, 16, 51)
f > qf(0.975, 16, 51)
```
Since our F Test Statistic is not larger and not smaller than the F Stat for alpha, we do not have enough evidence to reject the null hypothesis that the variances are equal.  It does not appear that the the Winter months experience a less varied number of arsons than the other 9 months.  

### 2) Are there more Auto Thefts on Weekends over Weekdays?  
```{r, message = FALSE, warning = FALSE}
auto_thefts <- crime %>%
                filter(Description %in% c("ROBBERY - CARJACKING", "AUTO THEFT"))
head(auto_thefts)
```
```{r, message= FALSE, warning = FALSE}
at_form <- auto_thefts %>%
                  mutate(CrimeDate= as.Date(CrimeDate, format = "%m/%d/%Y"), 
                         DateName = wday(CrimeDate, label = TRUE))
weekend <- at_form %>%
              filter(DateName %in% c("Sat", "Sun")) %>%
              group_by(CrimeDate, DateName) %>%
              summarize(Count = sum(`Total Incidents`))
              
weekday <- at_form %>%
              filter(!(DateName %in% c("Sat", "Sun"))) %>%
              group_by(CrimeDate, DateName) %>%
              summarize(Count = sum(`Total Incidents`))

ggplot(data = weekday, aes(x = Count)) + geom_histogram() + ggtitle("Weekday Distribution")
ggplot(data = weekend, aes(x = Count)) + geom_histogram() + ggtitle("Weekend Distribution")
```

With our data cleaned, we can now go about testing to see if the mean of the weekend set is larger than the mean of the weekday set.  But first... equal variance check.  Which, is just an F test:

H_0: Var_Weekday = var_Weekend
H_1: var_Weekday < var_weekend
```{r, warning=FALSE, message = FALSE}
#Weekday Variance
var(weekday$Count)
#df of Weekday
nrow(weekday)-1
#Weekend Variance
var(weekend$Count)
#df of Weekends
nrow(weekend)-1
```

Test Statistic
```{r, warning = FALSE, message = FALSE}
f_w <- var(weekday$Count)/var(weekend$Count)
f_w
```

Rejection Region:
```{r, message= FALSE, warning = FALSE}
up <- qf(0.975, 1479, 591) 
up
dwn <- qf(0.025, 1479, 591)
dwn
```

```{r, warning = FALSE, message = FALSE}
f_w > up
f_w < dwn
```
Conclusion: Since our F Stat was less than the upper rejection region and more than the lower rejections region, we do not have enough evidence to reject the hypothesis that the variances are equal.  It does not appear that the variances are different.   Now we can test the means.  

Hypotheses:
H_0: mean_weekday = mean_weekend
H_1: mean_weekday < mean_weekend

Test Statistic:
```{r, warning = FALSE, message = FALSE}
t.test(x = weekday$Count, y = weekend$Count)
```
Rejection Region
```{r, warning = FALSE, message = FALSE}
lower <- qt(0.05, 2070)
lower

-1.5301 < lower
```

Conclusion:
Since -1.5301 is greater than our rejection region, we do not have enough proof to reject our null hypothesis that the means are the same.  It does not appear that the there are more Auto thefts on weekends in comparison to weekdays.  


### 3)	On a given night are there more shootings inside a residence than outside?
```{r, message = FALSE, warning = FALSE}
shootings <- crime %>%
#              mutate(CrimeTime = strptime(CrimeTime, format = "%H:%M")) %>%
              filter(Description == "SHOOTING", CrimeTime > "17:00") %>%
              group_by(CrimeDate, `Inside/Outside`) %>%
              summarize(Count = sum(`Total Incidents`))
head(shootings)
dim(shootings)

ggplot(shootings, aes(x = Count)) + geom_histogram() + facet_grid(~ `Inside/Outside`)
```
With non-normal distributions, our route that we should run down is to check to see if the medians are different between the two groups. Using the Wilcoxon Rank Sum test, we'll see what if the outisde median is larger than the inside median.  

Hypothesis:
H_0: M_Inside = M_Outside
H_1: M_Inside > M_Outside
```{r, warning = FALSE, message = FALSE}
w <- wilcox.test(Count ~ `Inside/Outside`, data = shootings, alternative = "greater")
```

Test Statistic
```{r, warning = FALSE, message = FALSE}
w$statistic
```

Rejection Region
```{r, warning = FALSE, echo= FALSE}
w$p.value < 0.05
```

Conclusion/Interpretation:
Since our p-value is greater than 0.05, we do not have enough evidence to reject the null hypothesis that the Medians are the same.  It does not appear the there are more shootings inside a residence than outside.  

###4)	On a given day if you are assaulted,  is it more likely to be a common assault? 

Hypotheses:
H_0: Mean_aggAssault = Mean_CommonAssault
H_1: Mean_aggAssault < Mean_CommonAssault

```{r, message = FALSE, warning = FALSE}
assaults <- crime %>%
              filter(Description %in% c("AGG. ASSAULT", "COMMON ASSAULT")) %>%
              select(CrimeDate, Description, `Total Incidents`) %>%
              group_by(CrimeDate, Description) %>%
              summarize(Total = sum(`Total Incidents`)) %>%
              ungroup()

day_merge <- assaults %>%
              group_by(CrimeDate) %>%
              summarize(Count = sum(Total))

assaults <- assaults %>%
              group_by(CrimeDate) %>%
              left_join(day_merge) %>%
              mutate(percent = Total/Count) %>%
              ungroup() %>%
              mutate(CrimeDate = as.Date(CrimeDate, format = "%m/%d/%Y")) %>%
              arrange(desc(CrimeDate))

ggplot(data = assaults, aes(x =percent)) + geom_histogram() + facet_grid(~Description)
```
```{r, message = FALSE, warning = FALSE}
assaults_split <- t.test(formula = percent ~ Description, data = assaults, alternative = "less")
```
Test Statistic/p-value
```{r, message = FALSE, warning = FALSE}
assaults_split$statistic

assaults_split$p.value
```

Conclusion:
Since our p-value is less than 0.05, we have sufficient evidence to reject the null hypothesis that the means are the same.  It appears that the Mean percent of the Aggravated Assault group is less than the Mean percent of the Common Assault.  

###5)	Is there a District with a distinctly higher number of Burglary's in the Summer Months?  If so, which are significantly different?  
H_0: means are all the same
H_1: at least one mean is different
```{r, message = FALSE, warning = FALSE}
summer_burglaries <- crime %>%
                      filter(substr(CrimeDate, 1,1) %in% c('6','7','8'), Description == "BURGLARY") %>%
                      mutate(CrimeDate <- as.Date(CrimeDate, format = "%m/%d/%Y")) %>%
                      mutate(YearMon = as.yearmon(CrimeDate,  "%m/%d/%Y")) %>%
                      group_by(District, YearMon) %>%
                      summarize(Count = sum(`Total Incidents`)) %>%
                      filter(District != "NA") %>%
                      ungroup()

ggplot(data= summer_burglaries, aes(x = Count)) + geom_histogram() + facet_wrap(~ District)
```

Test Choice:
Since there is a mess of distributions that appear to fit an ANOVA model, I'll use the ANOVA test to see if there's one mean that's different.  
```{r, message = FALSE, warning = FALSE}
summer_burglaries <- summer_burglaries %>%
                      mutate(District = as.factor(District))


sum_burg_anova_check <- aov(Count ~ District, data = summer_burglaries)

y <- quantile(sum_burg_anova_check$residuals[!is.na(sum_burg_anova_check$residuals)], c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope = diff(y)/diff(x)
int <- y[1L] - slope*x[1L]


norm_res <- ggplot(data = sum_burg_anova_check, aes(x = sum_burg_anova_check$residuals)) + geom_histogram(bins = 6) + xlab("Residuals") + ggtitle("Residuals")


resid_jitter <- ggplot(data = sum_burg_anova_check, aes(x = sum_burg_anova_check$fitted.values, y = sum_burg_anova_check$residuals)) + geom_jitter() +  xlab("Group Mean") + ylab("Residuals") + ggtitle("Residuals vs. Predicted Mean")


qq <- ggplot(data = sum_burg_anova_check) + stat_qq(aes(sample = sum_burg_anova_check$residuals), alpha = 0.5) + 
    geom_abline(slope = slope, intercept = int, color = "blue") + ggtitle("Q-Q Plot")


res_sum <- as.table(summary(sum_burg_anova_check$residuals), nrow= 2, ncol = 6)
grid.arrange(resid_jitter, norm_res, qq, nrow = 2, ncol = 2)
```

Checking ANOVA/Test Statistic/p-value
```{r, message = FALSE, warning = FALSE}
summary(sum_burg_anova_check)
```

Since our p-value is considerably less than 0.05, we can conclude that it appears that one mean is different than the other.  We will proceed with Tukey's HSD to show which district is different from another.  

```{r, message = FALSE, warning = FALSE}
thsd_sum_burg <- TukeyHSD(sum_burg_anova_check)
thsd_sum_burg
```

\begin{itemize} 

\item The Northeastern District has distinctly larger number of burglaries than all other groups.

\item The Northwestern District has a distinctly larger number of burglaries than the Western, Northern, and Eastern.

\item The Southern District has a distinctly larger number of burglaries in the Summer months over the Central, Eastern, and the Southwest.

\item The Southwest District has a distinctly larger number of burglaries in the Summer months over the Eastern, Northern, and the Western districts.  

\item The Western District has a distinctly larger number of burglaries in the Summer months over the Northern and southern Districts.

\item The Nothern District has a distincly larger number of burglaries in the Summer months over the Central and Eastern Districts.  

\item The Southeastern District has a distinctly larger number of burglaries in the Summer months over the Central and Eastern Districts.

\end{itemize}