---
title: "Chapter 10 HW"
author: "Kyle Ligon"
date: "April 27, 2018"
output: pdf_document
---

10.14
a) Would it be appropriate to use a normal approximation in conducting a
statistical test of the research hypothesis that over half of persons suffering
from chonic pain are over 50 years of age?
```{r, message= FALSE, warning = FALSE}
(424/800)*(800) > 5
(376/800)*(800) > 5
```
Yes, it is appropriate.  


b)Using the data in the survey, is there substantial evidence ($\alpha$ = 0.05) 
that more than half of persons suffering from chronic pain are over 50 years
of age?
```{r, warning = FALSE, message = FALSE}
old <- prop.test(x = 484, n = 800, p = 0.5, alternative =  "greater", correct = FALSE)
old
```

c) Place a 95% confidence interval on the proportion of person suffering from 
chronic pain that are over 50 years of age.  
```{r, warning = FALSE, message = FALSE}
0.605 - 1.96*(sqrt(0.605*0.395/800))
0.605 + 1.96*(sqrt(0.605*0.395/800))
```

10.18
a) Place a 95% confidence interval on p1-p2, the difference in the proportions of customers purchasing lawnmowers with and without the warranty.  
```{r, warning=FALSE, message = FALSE}
mower <- prop.test(x = c(10, 4), n = c(25, 25), alternative = "two.sided", 
                   correct = FALSE)
mower$conf.int
```

b) Test the research hypothesis that offering the warranty will increase the proportion of customers who will purchase a mower.  Use $\alpha$ = 0.05.  
```{r, warning = FALSE, message = FALSE}
mower.test <- prop.test(x = c(10,4), n = c(25,25), alternative = "greater",
                        correct = FALSE)
mower.test
```

c) Are the conditions for using a large-sample test to answer the question in part b) satisfied?  If not, apply an exact procedue.  
```{r, warning = FALSE, message = FALSE}
0.4*25 > 5
0.6*25 > 5
0.16*25 > 5
0.84*25 > 5

x <- matrix(c(10, 4, 15, 21), byrow = FALSE, nrow = 2, ncol = 2)
fisher.test(x, alternative = "greater")
```

d) Based on your results from parts a) and b), should the dealer offer the warranty?
The dealer should not offer the warranty.  The test stat isn't statistically significant at alpha = 0.05.   


10.42 (b,d)
b) Is the promotion decision for the fireman related to the age of the fireman? Use $\alpha$ = 0.05.
```{r, message = FALSE, warning = FALSE}


```


d) What are some other variables, besides agem that needed to be addressed in an age discrimination analysis?  
```{r, message = FALSE, warning = FALSE}


```

10.43
a) Is the age of the fireman related to whethere or not the firmae is promoted?  Use $\alpha$ = 0.05.  
```{r, message = FALSE, warning = FALSE}

```

b) Is your conclusion concerning age discrimination different from your conclusion using the data in Exercise 10.42?  
```{r, message = FALSE, warning = FALSE}

```