---
title: "Chapter 14 and 15 HW"
author: "Kyle Ligon"
date: "March 30, 2018"
output:
  pdf_document: default
  html_document: default
---
14.8 (a) Assess ANOVA assumptions using the graph from PROC MIXED.

```{r, warning = FALSE, echo = FALSE, message = FALSE}
library(tidyverse)
library(grid)
library(gridExtra)
library(kableExtra)
library(multcomp)
a1_p1 <- data.frame(matrix(c(rep("a1", 10), rep("p1", 10), 19, 36, 40, 30, 4, 10, 30, 5, 34, 21), ncol = 3, nrow = 10))
a2_p1 <- data.frame(matrix(c(rep("a2", 10), rep("p1", 10), 19, 35, 22, 28, 1, 27, 27, 16, 3, 18), ncol = 3, nrow = 10))
a3_p1 <- data.frame(matrix(c(rep("a3", 10), rep("p1", 10), 37, 6, 28, 4, 32, 16, 8, 41, 29, 18), ncol = 3, nrow = 10))
a1_p2 <- data.frame(matrix(c(rep("a1", 10), rep("p2", 10), 39, 18, 32, 22, 16, 2, 36, 43, 7, 16), ncol = 3, nrow = 10))
a2_p2 <- data.frame(matrix(c(rep("a2", 10), rep("p2", 10), 30, 47, 6, 27, 44, 26, 33, 48, 23, 21), ncol = 3, nrow = 10))
a3_p2 <- data.frame(matrix(c(rep("a3", 10), rep("p2", 10), 51, 52, 43, 48, 39, 33, 56, 43, 40, 51), ncol = , nrow = 10))
frame <- rbind(a1_p1, a2_p1, a3_p1, a1_p2, a2_p2, a3_p2)
colnames(frame) <- c("ageGroup", "products", "att_spans")
frame$att_spans <- as.numeric(frame$att_spans)
anova_mod <- aov(att_spans ~ ageGroup * products, data = frame)
y <- quantile(anova_mod$residuals[!is.na(anova_mod$residuals)], c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope = diff(y)/diff(x)
int <- y[1L] - slope*x[1L]


norm_res <- ggplot(data = anova_mod, aes(x = anova_mod$residuals)) + geom_histogram(bins = 6) + xlab("Residuals") + ggtitle("Residuals")


resid_jitter <- ggplot(data = anova_mod, aes(x = anova_mod$fitted.values, y = anova_mod$residuals)) + geom_jitter() +  xlab("Group Mean") + ylab("Residuals") + ggtitle("Residuals vs. Predicted Mean")


qq <- ggplot(data = anova_mod) + stat_qq(aes(sample = anova_mod$residuals), alpha = 0.5) + 
    geom_abline(slope = slope, intercept = int, color = "blue") + ggtitle("Q-Q Plot")


res_sum <- as.table(summary(anova_mod$residuals), nrow= 2, ncol = 6)
grid.arrange(resid_jitter, norm_res, qq, nrow = 2, ncol = 2)
```

14.8 (b) Perform an ANOVA to determine if there is an interaction between the age group and types of products;

```{r, echo = FALSE, messsage = FALSE, warning = FALSE}
#INteraction Term
qf(0.95, 2, 54)
#Age Group
qf(0.95, 2, 56)
#Products
qf(0.95, 1, 56)

anova_mod_noI <- aov(data = frame, formula = att_spans ~ ageGroup + products)
```

(e) Report significantly different pairs using Tukey's W and $\alpha$ = 0:05; REMEMBER: if there is an interaction present, we must account for that when performing post-hoc testing
```{r, warning= FALSE, message = FALSE}
# if there was an interaction, we would do this.  
frame_Tukey <- frame %>%
                mutate(Combination = paste0(ageGroup, "-", products))
new_anova_mod <- aov(data = frame_Tukey, formula = att_spans ~ Combination)

TukeyHSD(new_anova_mod)

#but since there's not, we can just do the Tukey W on the old ANOVA model
TukeyHSD(anova_mod_noI)
```
From this we can tell that a2 and a3 differes from a1.  Additionally, p2 is different from p1.  

15.10 (a) Assess ANOVA assumptions using the graph from PROC MIXED.


```{r, echo = FALSE, warning = FALSE, message = FALSE}
# creating the data frame
car_model <- c(rep("cm1", 1), rep("cm2", 1), rep("cm3",1), rep("cm4", 1))
driver <- c(rep("d1",4), rep("d2", 4), rep("d3", 4), rep("d4", 4))
seed <- c("A", "B", "C", "D", "B", "C", "D", "A", "C", "D", "A", "B", "D", "A", "B", "C")
mileage <- c(15.5, 16.3, 10.5, 14.0, 33.8, 26.4, 31.5, 34.5, 13.7, 19.1, 17.5, 19.7, 29.2, 22.5, 30.1, 21.6)
petrol <- data.frame(car_model, driver, seed, mileage)

petrol <- petrol %>%
            mutate(car_model = as.factor(car_model), 
                   driver = as.factor(driver),
                   seed = as.factor(seed)) %>%
            arrange(car_model)


petrol_anova_mod <- aov(data = petrol, formula = mileage ~ car_model + driver + seed)
y1 <- quantile(petrol_anova_mod$residuals[!is.na(petrol_anova_mod$residuals)], c(0.25, 0.75))
x1 <- qnorm(c(0.25, 0.75))
slope1 = diff(y1)/diff(x1)
int1 <- y1[1L] - slope1*x1[1L]


norm_res1 <- ggplot(data = petrol_anova_mod, aes(x = petrol_anova_mod$residuals)) + geom_histogram(bins = 6) + xlab("Residuals") + ggtitle("Residuals")


resid_jitter1 <- ggplot(data = petrol_anova_mod, aes(x = petrol_anova_mod$fitted.values, y = petrol_anova_mod$residuals)) + geom_jitter() +  xlab("Group Mean") + ylab("Residuals") + ggtitle("Residuals vs. Predicted Mean")


qq1 <- ggplot(data = petrol_anova_mod) + stat_qq(aes(sample = petrol_anova_mod$residuals), alpha = 0.5) + 
    geom_abline(slope = slope1, intercept = int1, color = "blue") + ggtitle("Q-Q Plot")


res_sum1 <- as.table(summary(petrol_anova_mod$residuals), nrow= 2, ncol = 6)
grid.arrange(resid_jitter1, norm_res1, qq1, nrow = 2, ncol = 2)

```
(c) If there is a difference per part (b), use Tukey's W to determine the significantly different pairs; $\alpha$ = 0:05
```{r, echo = FALSE, message = FALSE, warning = FALSE}
TukeyHSD(petrol_anova_mod)
```
e) Determine if there is a difference between gasoline blends using ANOVA for completely randomized designs (i.e., ignore the blocking factors); $\alpha$ = 0:05}


```{r, echo = FALSE, warning = FALSE, message = FALSE}
pretrol_noBlock <- aov(data = petrol, formula = mileage ~ seed)
y2 <- quantile(pretrol_noBlock$residuals[!is.na(pretrol_noBlock$residuals)], c(0.25, 0.75))
x2 <- qnorm(c(0.25, 0.75))
slope2 = diff(y2)/diff(x2)
int2 <- y2[1L] - slope2*x2[1L]


norm_res2 <- ggplot(data = pretrol_noBlock, aes(x = pretrol_noBlock$residuals)) + geom_histogram(bins = 6) + xlab("Residuals") + ggtitle("Residuals")


resid_jitter2 <- ggplot(data = pretrol_noBlock, aes(x = pretrol_noBlock$fitted.values, y = pretrol_noBlock$residuals)) + geom_jitter() +  xlab("Group Mean") + ylab("Residuals") + ggtitle("Residuals vs. Predicted Mean")


qq2 <- ggplot(data = pretrol_noBlock) + stat_qq(aes(sample = pretrol_noBlock$residuals), alpha = 0.5) + 
    geom_abline(slope = slope, intercept = int, color = "blue") + ggtitle("Q-Q Plot")


res_sum <- as.table(summary(pretrol_noBlock$residuals), nrow= 2, ncol = 6)
grid.arrange(resid_jitter2, norm_res2, qq2, nrow = 2, ncol = 2)

summary(pretrol_noBlock)

qf(0.95, 3, 12)

```

