\documentclass{article}

\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}

\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{titlesec}
\usepackage{amsmath}

\setcounter{secnumdepth}{4}

\hypersetup{
    colorlinks=true,     
    urlcolor=magenta
}

\renewcommand{\qedsymbol}{\rule{0.7em}{0.7em}}

\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\setlength{\parskip}{0em}

\newenvironment{blockquote}{%
  \par%
  \vskip1em
  \leftskip=2em\rightskip=2em%
  \noindent\ignorespaces}{%
  \par\vskip1em}

\newenvironment{blockquote2}{%
	\par%
	\vskip1em
	\leftskip=4em\rightskip=4em%
	\noindent\ignorespaces}{%
	\par\vskip1em}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LO]{STA5176}
\fancyhead[RO]{Kyle Ligon}
\fancyfoot[LO]{Chapter 6}
\fancyfoot[RO]{\thepage}
 
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\begin{document}
\section*{Chapter 6 Homework}
\subsection*{Due 2-18-2018}
\subsubsection*{Problem 6.13}
\subsubsection*{a) Complete a Hypothesis Test for $\mu_1$-$\mu_2$; $\alpha$ = 0.05}
Hypothesis
\begin{blockquote}
	$H_0: \mu_1 - \mu_2 = 0$

	$H_{A}: \mu_1 - \mu_2 \neq 0$
\end{blockquote}

Assumptions:
\begin{blockquote}
	1) Independent Samples.  

	2) Equal Variances.  ($\sigma_F^{2} = 1.4136,  \sigma_M^{2} = 1.0077$)
\end{blockquote}

Test Statistic: 
\begin{eqnarray}
	t_0 = \frac{\bar{y_1}-\bar{y_2}-D_0}{s_p\sqrt{\frac{1}{n_1}+\frac{1}{n_2}}} \nonumber \\
	t_0 = \frac{(8.5333 - 9.6833)-0}{1.0719\sqrt{0.0417+0.0278}} \nonumber \\
	t_0 = \frac{-1.15}{0.2826} \nonumber \\
	t_0 = -4.0708 \nonumber
\end{eqnarray}
Rejection Region
\begin{blockquote}
$|t_0| \geq t_{\frac{\alpha}{2}, 58};  t_{\frac{\alpha}{2}, 58} = 2.0017$

Thus, $|-4.0708| = 4.0708 \geq 2.0017$
\end{blockquote}

P-Value
\begin{blockquote}
The p-value on a t-score of -4.0708 = $7.1822x10^{-5}.$   

Therefore, with out p-value is less than our $\alpha$ of 0.025.  
\end{blockquote}

Conclusion
\begin{blockquote}
Since the absolute value of our t-score is greater than our Rejection Bound, there is sufficient evidence to reject our Null Hypothesis.  There is evidence to suggest that the two mean pays between the Male and Female group are different.  
\end{blockquote}

\subsection*{b) Complete a 95\% C.I. for $\mu_1 - \mu_2$}
Assumptions
\begin{blockquote}
1) We are still under the assumption that these two groups were chosen independently.

2) We are also under the assumption that the Variances are equal and holding from the last section.  
\end{blockquote}
Confidence Interval Equation
\begin{eqnarray}
	C.I. = \bar{y_1}-\bar{y_2} \pm t_{\frac{\alpha}{2}, df}(\frac{s_1^{2}}{\sqrt{n_1}} + \frac{s_2^{2}}{\sqrt{n_2}}) \nonumber \\
	C.I. =  (8.5333 - 9.6833) \pm 2.0017(\frac{1.4136}{4.8990}+\frac{1.0077}{6}) \nonumber \\
	C.I. = -1.15 \pm 2.0017(0.4565) \nonumber \\ 
	C.I. = -1.15 \pm 0.9138 \nonumber \\
	C.I \approx (-2.0638, -0.2362)  \nonumber 
\end{eqnarray}

Conclsion
\begin{blockquote}
Since 0 is not in our confidence interval, we can conclude we have strong enough evidence to suggest that the population mean pays between men and women at this firm are different.  This supports the hypothesis test we did in a).  
\end{blockquote}














\end{document}